paper

### 2024-09-24 inst/extdata/paperdata/paper.qmd
.

>>>>

## Columbia Case Study

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
#data("Columbia.RealCase")
print(Columbia.RealCase)

# Set metadata and formula for LimROTS analysis
meta.info <- c("groups" , "Age" , "gender" , "LRRK2.status" , "GBA.status")
B <- 1000  # Number of bootstrap samples
K <- dim(Columbia.RealCase)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "groups"
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

trace(LimROTS, edit = T)

limrots.result <- LimROTS(data.exp = Columbia.RealCase, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

saveRDS(limrots.result, "inst/extdata/paperdata/Columbia.RealCase.LimROTS.rds")
```

### Q Plot

```{r}
plot(limrots.result$q_values)
hist(limrots.result$q_values)
summary(limrots.result$q_values)
```

### Volcano Plot with ggplot2

```{r}
library(ggplot2)
# Create a data frame from the LimROTS results
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$logfc,
                                q.value = limrots.result$q_values$pvalues)

# Create a volcano plot
ggplot(limrots.result.df, aes(x = limrots.result$corrected.logfc, y = -log10(limrots.result$pvalue) )) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black")
```

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("Columbia.RealCase")
data <- assay(Columbia.RealCase)
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"
meta.info <- data.frame(colData(Columbia.RealCase), check.names = FALSE, row.names = row.names(colData(Columbia.RealCase)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("groups1-groups2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="groups1-groups2" , number = "Inf")

# Create a volcano plot
ggplot(limma.result, aes(x = logFC, y = -log10(P.Value))) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black")
```
